---
title: "myHW"
author: "min cheng"
date: "9/22/2023"
output: html_document
---
```{r}

```

# Heading(no hash)# library(openxlsx)  
## Heading 2 (two hashes)
### Sub Heading  (3 hashes)
#### Sub Heading2  (4 hashes)
##### Bold text  (5 hashes)
###### Bold text 2  (6 hashes)
###### End





# Install and load the readxl package
chooseCRANmirror(ind = 1)  # 选择一个 CRAN 镜像仓库
install.packages("readxl")
library(readxl)

```





# Specify the path to your Excel file
```{r}
excel_file <- "C:/Users/mchen/OneDrive/Documents/R forecasting/Typical_Employee_Survey_Data.xlsx"
```

```{r}
# 安装 readxl 包（如果还没有安装的话）
install.packages("readxl", repos = "http://cran.rstudio.com/")


library(readxl)

excel_path <- "C:/Users/mchen/OneDrive/Documents/R forecasting/Typical_Employee_Survey_Data.xlsx"  # 请确保替换为实际的文件路径

my_data <- read_excel(excel_path)

print(my_data)
```

---
# Read an Excel file
```{r}
excel_data <- read_excel("C:/Users/mchen/OneDrive/Documents/R forecasting/Typical_Employee_Survey_Data.xlsx")
```

# Print the data frame
```{r}
print(data)
```


# Read the Excel file into R without using the first row as column names
```{r}
data <- read_xlsx(excel_file, col_names = FALSE)
print(data)
```


# Change data column names
```{r}
colnames(data)[1:11] <- c("Age", "Gender", "Department","job satisfaction","longevity","attitudes","measurement 4","measurement 5","measurement 6","measurement 7","measurement 8")

print(data)
```

# Convert the "Age" column to numeric (if it's not already)
```{r}
data$Age <- as.numeric(data$Age)
```

# Find the minimum value of the "Age" column
```{r}
min_value <- min(data$Age)
```

# Print the minimum value
```{r}
print(min_value)
```


```{r}
range(data[, 1])
StatRange = max(data[, 1]) - min(data[, 1])
c

# Display the result
```{r}
cat("StatRange:", StatRange, "\n")
```
# Calculate the mean of column 1 (Age) excluding the header
```{r}
mean_age <- mean(data[, 1], na.rm = TRUE)

print(mean_age)
```

# Filter out rows with non-numeric or missing values in column 1 (Age)
```{r}
data_cleaned <- data[!is.na(data$Age) & is.numeric(data$Age), ]
```

# Calculate the mean of the cleaned data
```{r}
mean_age <- mean(data_cleaned$Age)
```

# Print the mean value
```
print(mean_age)
```

# Filter out rows with non-numeric or missing values in column 1 (Age)
```{r}
data_cleaned <- data[!is.na(data$Age) & is.numeric(data$Age), ]
```

# Calculate the mean of the cleaned data
```{r}
sd_age <- sd(data_cleaned$Age)
print(sd_age)
```

```{r}
data_cleaned <- data[!is.na(data$Age) & is.numeric(data$Age), ]
var_age <- var(data_cleaned$Age)
print(var_age)
```

# Remove the header row
```{r}
data_no_header <- data[-1, ]
```

# Calculate the variance of the "Age" column without the header
```{r}
variance_age <- var(data_no_header$Age)
print(variance_age)
```

# Calculate the standard deviation of the "Age" column without the header
```{r}
std_dev_age <- sqrt(var(data_no_header$Age))
print(std_dev_age)
```

# Calculate the five-number summary of the "Age" column without the header
```
five_num_summary <- fivenum(data_no_header$Age)
print(five_num_summary)
```

# Calculate the interquartile range (IQR) of the "Age" column without the header
```{r}
iqr_age <- IQR(data_no_header$Age)
print(iqr_age)
```

# Calculate quantiles (e.g., quartiles) of the "Age" column without the header
```{r}
quantiles_age <- quantile(data_no_header$Age)
print(quantiles_age)
```

```{r}
summary(data$Age)
summary(data$Gender)
summary(data$Department)
summary(data$'longevity')
summary(data$'attitudes')
summary(data$'measurement4')
summary(data$'measurement5')
summary(data$'measurement6')
summary(data$'measurement7')
summary(data$'measurement8')
```

```{r}
boxplot.stats(data$Age)
```



# Specify the path to your Excel file
```{r}
excel_file <- "C:/Users/mchen/OneDrive/Documents/R forecasting/Typical_Employee_Survey_Data.xlsx"
```


# Load the required library for reading Excel files
```{r}
library(readxl)
data <- read_excel(excel_file)
nrow(data)

print(data)# Print the data frame

colnames(data)
# Print the data frame
```

# Change data column names
```{r}
colnames(data)[1:11] <- c("Age", "Gender", "Department","job satisfaction","longevity","attitudes","measurement 4","measurement 5","measurement 6","measurement 7","measurement 8")

colnames(data)

print(data)
```

# Convert specific columns to factors
```{r}
data$Age <- factor(data$Age)
data$Gender <- factor(data$Gender)
```


# Convert all columns to factors
```
data <- as.data.frame(lapply(data, as.factor))
```

#check if convertion result
```{r}
str(data)
```

# Create a bar plot for the 'Age' column
```{r}
barplot(table(data$Age), main="Age Distribution", xlab="Age", ylab="Frequency")
```



summary(data)
```{r}
boxplot.stats(data$Age)$out
```


# Convert the "Age" column back to numeric
```{r}
data$Age <- as.numeric(as.character(data$Age))
outliers <- boxplot.stats(data$Age)$out
range_of_age <- range(data$Age)
```

# Print the results
```{r}
print(outliers)
print(range_of_age)
```


#pieplot
```{r}
# Using "Gender" column to label the boxes
boxplot(data$Age, main = "Age by Gender", xlab = "Gender", ylab = "Age", col = "orange", names.arg = data$Gender)

# Using "Department" column to label the boxes
boxplot(data$Age, main = "Age by Department", xlab = "Department", ylab = "Age", col = "blue", names.arg = data$Department)
```


-----
# Sample data
```{r}
data <- data.frame(
  Department = c(2, 2, 1, 1, 2, 2, 1, 2, 1, 1, 1, 2, 2, 1, 3, 2, 2, 2, 1, 1, 1, 4, 1, 2, 2, 2, 1, 4, 1, 1, 2, 1, 1, 3, 1, 1, 2, 1, 3, 2, 2, 1, 4, 2, 1, 1, 1, 1, 4, 2, 2, 1, 2, 2, 1, 1, 1, 3, 2, 1, 4, 2, 2, 1, 1, 2, 1, 1, 2, 1, 1, 1, 2, 2, 3, 2, 2, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 1, 3, 2, 2, 1, 1, 2, 2, 1, 2, 1, 1, 1, 1, 1, 1, 1, 2, 4, 1, 1, 1, 2, 1, 4, 1, 1, 2, 1, 2, 2, 1, 1, 1, 2),
  Attitudes = c(1, 5, 1, 3, 3, 1, 5, 2, 4, 2, 4, 2, 2, 1, 4, 5, 2, 4, 3, 5, 1, 4, 1, 1, 1, 2, 5, 5, 5, 5, 1, 1, 1, 2, 5, 5, 2, 5, 5, 2, 1, 2, 4, 2, 5, 5, 4, 4, 1, 1, 4, 4, 2, 3, 2, 1, 4, 4, 2, 4, 4, 2, 5, 2, 2, 2, 2, 1, 4, 1, 5, 4, 5, 3, 4, 5, 5, 5, 2, 4, 4, 5, 2, 5, 5, 2, 2, 2, 5, 5, 4, 5, 1, 4, 4, 5, 2, 2, 1, 5, 2, 5, 4, 4, 5, 4, 4, 5, 3, 5, 5, 5, 4, 5, 4, 5, 5, 4, 1, 5, 2, 1)
)
```

# Calculate average attitudes by department
```{r}
avg_attitudes <- tapply(data$Attitudes, data$Department, mean)
```
# Create an empty plot without plotting any points
plot(1, type = "n", xlim = c(1, length(unique(data$Department))), ylim = range(data$Attitudes), 
     xaxt = "n", xlab = "Department", ylab = "Attitudes", main = "Department vs. Attitudes")


lines(1:length(unique(data$Department)), avg_attitudes, type = "o", col = "blue", pch = 19)# Add lines to the plot


axis(1, at = 1:length(unique(data$Department)), labels = unique(data$Department))# Add x-axis labels
```



# another code of lineplot

```{r}
data$Attitudes <- as.integer(data$Attitudes)

avg_attitudes <- tapply(data$Attitudes, data$Department, mean)
```

#  Line Plot
```{r}
plot(unique(data$Department), avg_attitudes, type = "o", 
     xlab = "attitudes", ylab = "Average Department", 
     main = "Line Plot of Average Attitudes vs. Department",
     col = "blue", pch = 19)
```









####xy plot

# Load the lattice package (if not already loaded)
```{r}
library(lattice)

data <- data.frame(
  Age = c(35, 33, 23, 60, 35, 34, 61, 59, 37, 30, 34, 34, 27, 38, 41, 58, 34, 48, 26, 39, 29, 36, 25, 39, 40, 53, 39, 27, 35, 25, 29, 23, 40, 36, 64, 43, 28, 48, 52, 32, 23, 44, 36, 33, 52, 38, 34, 62, 36, 37, 39, 61, 20, 22, 36, 48, 58, 50, 24, 44, 30, 32, 32, 44, 34, 42, 40, 37, 32, 31, 44, 39, 30, 41, 39, 33, 25, 31, 41, 42, 33, 36, 39, 39, 62, 62, 34, 52, 40, 43, 41, 64, 26, 45, 33, 36, 45, 51, 38, 57, 45, 43, 37, 33, 51, 43, 42, 25, 40, 57, 38, 41, 32, 39, 43, 50, 49, 35, 22, 33, 29, 22),
  Longevity = c(3, 9, 1.5, 20, 3, 6, 0.75, 1.5, 3, 5, 3, 8, 7, 15, 1, 36, 1.5, 6, 3.5, 3, 16, 4.08, 2, 2, 11.83, 10, 1, 2, 10, 2.5, 1, 0.75, 4.33, 10, 7, 18, 0.16, 1.66, 0.08, 3, 1, 5, 9.5, 3.75, 1, 2.66, 5.5, 52.25, 1, 19, 10, 13, 3, 1, 7, 4, 12, 22.5, 1, 10, 2, 7, 12, 22, 4, 22, 2, 5, 11, 10, 0.66, 11, 11, 12, 9, 10, 3, 5.5, 2.33, 5, 1, 6, 16, 3.25, 27, 1.91, 2.08, 31.91, 6, 14, 4, 29, 1.5, 0.58, 7, 5, 21, 24, 6, 34, 4, 26, 5, 1, 23, 3, 6, 2.5, 11.25, 29.25, 2, 11, 1.5, 9, 5, 1, 1.5, 10, 1, 11, 2, 1.25),
  JobSatisfaction = c(4, 3, 1, 1, 1, 1, 1, 5, 5, 5, 3, 3, 5, 4, 1, 4, 1, 5, 4, 5, 5, 5, 4, 5, 1, 1, 5, 2, 1, 5, 5, 2, 5, 1, 4, 5, 5, 5, 5, 1, 1, 1, 1, 3, 5, 5, 5, 1, 5, 5, 5, 5, 4, 5, 5, 4, 4, 5, 5, 1, 5, 5, 1, 4, 5, 5, 5, 5, 5, 1, 4, 5, 1, 4, 4, 5, 4, 5, 5, 2, 5, 5, 4, 1, 2, 1, 4, 2, 5, 5, 5, 5, 4, 5, 1, 3, 5, 5, 1, 1, 5, 5, 5, 1, 5, 5, 5, 5, 5, 5, 5, 5, 2, 5, 3, 5, 4, 2, 5, 5, 5, 2)
)
```

# Create an xyplot
```{r}
xyplot(Age + Longevity ~ JobSatisfaction, data = data, 
       main = "Scatterplot of Age + Longevity vs. Job Satisfaction",
       xlab = "Job Satisfaction", ylab = "Age + Longevity",
       type = c("p", "smooth"), col = "blue")
warnings()
```
# Sample data (replace with your data)
```{r}
Longevity = c(3, 9, 1.5, 20, 3, 6, 0.75, 1.5, 3, 5, 3, 8, 7, 15, 1, 36, 1.5, 6, 3.5, 3, 16, 4.08, 2, 2, 11.83, 10, 1, 2, 10, 2.5, 1, 0.75, 4.33, 10, 7, 18, 0.16, 1.66, 0.08, 3, 1, 5, 9.5, 3.75, 1, 2.66, 5.5, 52.25, 1, 19, 10, 13, 3, 1, 7, 4, 12, 22.5, 1, 10, 2, 7, 12, 22, 4, 22, 2, 5, 11, 10, 0.66, 11, 11, 12, 9, 10, 3, 5.5, 2.33, 5, 1, 6, 16, 3.25, 27, 1.91, 2.08, 31.91, 6, 14, 4, 29, 1.5, 0.58, 7, 5, 21, 24, 6, 34, 4, 26, 5, 1, 23, 3, 6, 2.5, 11.25, 29.25, 2, 11, 1.5, 9, 5, 1, 1.5, 10, 1, 11, 2, 1.25)
job_satisfaction <- c(4, 3, 1, 1, 1, 1, 1, 5, 5, 5, 3, 3, 5, 4, 1, 4, 1, 5, 4, 5)
```

# Create a scatter plot
```{r}
plot(data$Longevity, data$job_satisfaction, 
     xlab="Longevity", ylab="Job Satisfaction",
     main="Scatter Plot of Longevity vs. Job Satisfaction",
     col="orange", pch=19)
```






       












