---
title: "myHW"
author: "min cheng"
date: "9/22/2023"
output: html_document
---
```{r}

```

# Heading(no hash)# library(openxlsx)  
## Heading 2 (two hashes)
### Sub Heading  (3 hashes)
#### Sub Heading2  (4 hashes)
##### Bold text  (5 hashes)
###### Bold text 2  (6 hashes)
###### End
```{r}

```
# library(openxlsx)  # For openxlsx package
data <- read_xlsx("C:/Users/mchen/OneDrive/Documents/R/Typical_Employee_Survey_Data.xlsx")

# Heading(no hash)# library(openxlsx)  
## Heading 2 (two hashes)
### Sub Heading  (3 hashes)
#### Sub Heading2  (4 hashes)
##### Bold text  (5 hashes)
###### Bold text 2  (6 hashes)
###### End
```{r}

```

# Install and load the readxl package
install.packages("readxl")
library(readxl)


# Specify the path to your Excel file
excel_file <- "C:/Users/mchen/OneDrive/Documents/R forecasting/Typical_Employee_Survey_Data.xlsx"

# Read an Excel file
excel_data <- read_excel("C:/Users/mchen/OneDrive/Documents/R forecasting/Typical_Employee_Survey_Data.xlsx")

# Print the data frame
print(data)



# Read the Excel file into R without using the first row as column names
data <- read_xlsx(excel_file, col_names = FALSE)

# Print the data frame
print(data)

## Summary Stats



# Change data column names
colnames(data)[1:11] <- c("Age", "Gender", "Department","job satisfaction","longevity","attitudes","measurement 4","measurement 5","measurement 6","measurement 7","measurement 8")


print(data)


# Find the minimum value of the age
min_value <- min(data[, 1])

# Print the minimum value
print(min_value)

range(data[, 1])
StatRange = max(data[, 1]) - min(data[, 1])

# Display the result
cat("StatRange:", StatRange, "\n")

# Calculate the mean of column 1 (Age) excluding the header
mean_age <- mean(data[, 1], na.rm = TRUE)

# Print the mean value
print(mean_age)
# Filter out rows with non-numeric or missing values in column 1 (Age)
data_cleaned <- data[!is.na(data$Age) & is.numeric(data$Age), ]

# Calculate the mean of the cleaned data
mean_age <- mean(data_cleaned$Age)

# Print the mean value
print(mean_age)

# Filter out rows with non-numeric or missing values in column 1 (Age)
data_cleaned <- data[!is.na(data$Age) & is.numeric(data$Age), ]

# Calculate the mean of the cleaned data
sd_age <- sd(data_cleaned$Age)
print(sd_age)


data_cleaned <- data[!is.na(data$Age) & is.numeric(data$Age), ]
var_age <- var(data_cleaned$Age)
print(var_age)

# Remove the header row
data_no_header <- data[-1, ]

# Calculate the variance of the "Age" column without the header
variance_age <- var(data_no_header$Age)
print(variance_age)

# Calculate the standard deviation of the "Age" column without the header
std_dev_age <- sqrt(var(data_no_header$Age))
print(std_dev_age)

# Calculate the five-number summary of the "Age" column without the header
five_num_summary <- fivenum(data_no_header$Age)
print(five_num_summary)

# Calculate the interquartile range (IQR) of the "Age" column without the header
iqr_age <- IQR(data_no_header$Age)
print(iqr_age)

# Calculate quantiles (e.g., quartiles) of the "Age" column without the header
quantiles_age <- quantile(data_no_header$Age)
print(quantiles_age)

summary(data$Age)
summary(data$Gender)
summary(data$Department)
summary(data$`job satisfaction`)
summary(data$'longevity')
summary(data$'attitudes')
summary(data$'measurement4')
summary(data$'measurement5')
summary(data$'measurement6')
summary(data$'measurement7')
summary(data$'measurement8')

summary(data$`job satisfaction`)

# "longevity"  summary 
summary(data$`longevity`)

# "attitudes" summary
summary(data$`attitudes`)

"measurement 4" summary
summary(data$`measurement 4`)



#  "measurement5"  summary 
summary(data$`measurement5`)

#  "measurement6" summary
summary(data$`measurement6`)

#  "measurement7" summary
summary(data$`measurement7`)

# "measurement8" summary
summary(data$`measurement8`)


boxplot.stats(data$Age)




# Specify the path to your Excel file
excel_file <- "C:/Users/mchen/OneDrive/Documents/R forecasting/Typical_Employee_Survey_Data.xlsx"

# Load the required library for reading Excel files
library(readxl)

# Read the Excel file into R
data <- read_excel(excel_file)

nrow(data)


# Print the data frame
print(data)

colnames(data)


# Change data column names
colnames(data)[1:11] <- c("Age", "Gender", "Department","job satisfaction","longevity","attitudes","measurement 4","measurement 5","measurement 6","measurement 7","measurement 8")

colnames(data)

print(data)

# Convert specific columns to factors
data$Age <- factor(data$Age)
data$Gender <- factor(data$Gender)


# Convert all columns to factors
data <- as.data.frame(lapply(data, as.factor))

#check if convertion result
str(data)

stem(data$Age)


summary(data)
boxplot.stats(data$Age)$out

range(data$Age)
StatRange = max(data$Age) - min(data$Age)

#pieplot
# Using "Gender" column to label the boxes
boxplot(data$Age, main = "Age by Gender", xlab = "Gender", ylab = "Age", col = "orange", names.arg = data$Gender)

# Using "Department" column to label the boxes
boxplot(data$Age, main = "Age by Department", xlab = "Department", ylab = "Age", col = "blue", names.arg = data$Department)

#pieplot
pie(data$Department)

-----
# Sample data
data <- data.frame(
  Department = c(2, 2, 1, 1, 2, 2, 1, 2, 1, 1, 1, 2, 2, 1, 3, 2, 2, 2, 1, 1, 1, 4, 1, 2, 2, 2, 1, 4, 1, 1, 2, 1, 1, 3, 1, 1, 2, 1, 3, 2, 2, 1, 4, 2, 1, 1, 1, 1, 4, 2, 2, 1, 2, 2, 1, 1, 1, 3, 2, 1, 4, 2, 2, 1, 1, 2, 1, 1, 2, 1, 1, 1, 2, 2, 3, 2, 2, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 1, 3, 2, 2, 1, 1, 2, 2, 1, 2, 1, 1, 1, 1, 1, 1, 1, 2, 4, 1, 1, 1, 2, 1, 4, 1, 1, 2, 1, 2, 2, 1, 1, 1, 2),
  Attitudes = c(1, 5, 1, 3, 3, 1, 5, 2, 4, 2, 4, 2, 2, 1, 4, 5, 2, 4, 3, 5, 1, 4, 1, 1, 1, 2, 5, 5, 5, 5, 1, 1, 1, 2, 5, 5, 2, 5, 5, 2, 1, 2, 4, 2, 5, 5, 4, 4, 1, 1, 4, 4, 2, 3, 2, 1, 4, 4, 2, 4, 4, 2, 5, 2, 2, 2, 2, 1, 4, 1, 5, 4, 5, 3, 4, 5, 5, 5, 2, 4, 4, 5, 2, 5, 5, 2, 2, 2, 5, 5, 4, 5, 1, 4, 4, 5, 2, 2, 1, 5, 2, 5, 4, 4, 5, 4, 4, 5, 3, 5, 5, 5, 4, 5, 4, 5, 5, 4, 1, 5, 2, 1)
)

# Calculate average attitudes by department
avg_attitudes <- tapply(data$Attitudes, data$Department, mean)

# Create an empty plot
plot(1, type = "n", xlim = c(1, length(unique(data$Department))), ylim = range(data$Attitudes), 
     xaxt = "n", xlab = "Department", ylab = "Attitudes", main = "Department vs. Attitudes")

# Add x-axis labels
axis(1, at = 1:length(unique(data$Department)), labels = unique(data$Department))

# Add lines to the plot
lines(1:length(unique(data$Department)), avg_attitudes, type = "o", col = "blue", pch = 19)


# another code of lineplot


data$Attitudes <- as.integer(data$Attitudes)

# avg attitude
avg_attitudes <- tapply(data$Attitudes, data$Department, mean)

#  Line Plot
plot(unique(data$Department), avg_attitudes, type = "o", 
     xlab = "attitudes", ylab = "Average Department", 
     main = "Line Plot of Average Attitudes vs. Department",
     col = "blue", pch = 19)





# Create a data frame with data
data <- data.frame(
  Value = c(2, 1, 1, 2, 2, 1, 2, 1, 1, 1, 2, 2, 1, 3, 2, 2, 2, 1, 1, 1, 4, 1, 2, 2, 2, 1, 4, 1, 1, 2, 1, 1, 3, 1, 1, 2, 1, 3, 2, 2, 1, 4, 2, 1, 1, 1, 1, 4, 2, 2, 1, 2, 2, 1, 1, 1, 3, 2, 1, 4, 2, 2, 1, 1, 2, 1, 1, 2, 1, 1, 1, 2, 2, 3, 2, 2, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 1, 3, 2, 2, 1, 1, 2, 2, 1, 2, 1, 1, 1, 1, 1, 1, 1, 2, 4, 1, 1, 1, 2, 1, 4, 1, 1, 2, 1, 2, 2, 1, 1, 1, 2)
)

# Create a function to map values to departments
map_to_department <- function(value) {
  if (value == 1) {
    return("dept1")
  } else if (value == 2) {
    return("dept2")
  } else if (value == 3) {
    return("dept3")
  } else if (value == 4) {
    return("dept4")
  } else {
    return("Unknown")  # Handle other values
  }
}

# Use the function to map values to departments in the data frame
data$Department <- sapply(data$Value, map_to_department)

# Print frequency table
print(table(data$Department))

# Calculate proportions
prop_table <- prop.table(table(data$Department))

# Create a pie chart
pie(prop_table, labels = NULL, main = "Department Distribution", col = rainbow(length(prop_table)))

# Add a legend to the side
legend("right", legend = names(prop_table), fill = rainbow(length(prop_table)))




boxplot(data$Age)
boxplot(data$Gender)skip the non-numerical

# Filter out non-numerical values in the Gender column
data_numeric <- data[!is.na(as.numeric(data$Gender)), ]

# Create a boxplot for the numerical values in the Gender column
hist(as.numeric(data_numeric$Gender))





#xy plot

# Load the lattice package (if not already loaded)
library(lattice)


data <- data.frame(
  Age = c(35, 33, 23, 60, 35, 34, 61, 59, 37, 30, 34, 34, 27, 38, 41, 58, 34, 48, 26, 39, 29, 36, 25, 39, 40, 53, 39, 27, 35, 25, 29, 23, 40, 36, 64, 43, 28, 48, 52, 32, 23, 44, 36, 33, 52, 38, 34, 62, 36, 37, 39, 61, 20, 22, 36, 48, 58, 50, 24, 44, 30, 32, 32, 44, 34, 42, 40, 37, 32, 31, 44, 39, 30, 41, 39, 33, 25, 31, 41, 42, 33, 36, 39, 39, 62, 62, 34, 52, 40, 43, 41, 64, 26, 45, 33, 36, 45, 51, 38, 57, 45, 43, 37, 33, 51, 43, 42, 25, 40, 57, 38, 41, 32, 39, 43, 50, 49, 35, 22, 33, 29, 22),
  Longevity = c(3, 9, 1.5, 20, 3, 6, 0.75, 1.5, 3, 5, 3, 8, 7, 15, 1, 36, 1.5, 6, 3.5, 3, 16, 4.08, 2, 2, 11.83, 10, 1, 2, 10, 2.5, 1, 0.75, 4.33, 10, 7, 18, 0.16, 1.66, 0.08, 3, 1, 5, 9.5, 3.75, 1, 2.66, 5.5, 52.25, 1, 19, 10, 13, 3, 1, 7, 4, 12, 22.5, 1, 10, 2, 7, 12, 22, 4, 22, 2, 5, 11, 10, 0.66, 11, 11, 12, 9, 10, 3, 5.5, 2.33, 5, 1, 6, 16, 3.25, 27, 1.91, 2.08, 31.91, 6, 14, 4, 29, 1.5, 0.58, 7, 5, 21, 24, 6, 34, 4, 26, 5, 1, 23, 3, 6, 2.5, 11.25, 29.25, 2, 11, 1.5, 9, 5, 1, 1.5, 10, 1, 11, 2, 1.25),
  JobSatisfaction = c(4, 3, 1, 1, 1, 1, 1, 5, 5, 5, 3, 3, 5, 4, 1, 4, 1, 5, 4, 5, 5, 5, 4, 5, 1, 1, 5, 2, 1, 5, 5, 2, 5, 1, 4, 5, 5, 5, 5, 1, 1, 1, 1, 3, 5, 5, 5, 1, 5, 5, 5, 5, 4, 5, 5, 4, 4, 5, 5, 1, 5, 5, 1, 4, 5, 5, 5, 5, 5, 1, 4, 5, 1, 4, 4, 5, 4, 5, 5, 2, 5, 5, 4, 1, 2, 1, 4, 2, 5, 5, 5, 5, 4, 5, 1, 3, 5, 5, 1, 1, 5, 5, 5, 1, 5, 5, 5, 5, 5, 5, 5, 5, 2, 5, 3, 5, 4, 2, 5, 5, 5, 2)
)

# Create an xyplot
xyplot(Age + Longevity ~ JobSatisfaction, data = data, 
       main = "Scatterplot of Age + Longevity vs. Job Satisfaction",
       xlab = "Job Satisfaction", ylab = "Age + Longevity",
       type = c("p", "smooth"), col = "blue")
warnings()

# Sample data (replace with your data)
Longevity = c(3, 9, 1.5, 20, 3, 6, 0.75, 1.5, 3, 5, 3, 8, 7, 15, 1, 36, 1.5, 6, 3.5, 3, 16, 4.08, 2, 2, 11.83, 10, 1, 2, 10, 2.5, 1, 0.75, 4.33, 10, 7, 18, 0.16, 1.66, 0.08, 3, 1, 5, 9.5, 3.75, 1, 2.66, 5.5, 52.25, 1, 19, 10, 13, 3, 1, 7, 4, 12, 22.5, 1, 10, 2, 7, 12, 22, 4, 22, 2, 5, 11, 10, 0.66, 11, 11, 12, 9, 10, 3, 5.5, 2.33, 5, 1, 6, 16, 3.25, 27, 1.91, 2.08, 31.91, 6, 14, 4, 29, 1.5, 0.58, 7, 5, 21, 24, 6, 34, 4, 26, 5, 1, 23, 3, 6, 2.5, 11.25, 29.25, 2, 11, 1.5, 9, 5, 1, 1.5, 10, 1, 11, 2, 1.25)
job_satisfaction <- c(4, 3, 1, 1, 1, 1, 1, 5, 5, 5, 3, 3, 5, 4, 1, 4, 1, 5, 4, 5)

# Create a scatter plot
plot(data$Longevity, data$job_satisfaction, 
     xlab="Longevity", ylab="Job Satisfaction",
     main="Scatter Plot of Longevity vs. Job Satisfaction",
     col="orange", pch=19)






       












StatRange
mean(myDataFrame$Age)
sd(myDataFrame$Age)
var(myDataFrame$Age)
sqrt(var(myDataFrame$Age)
fivenum(myDataFrame$Age,)
IQR(myDataFrame$Age)
quantile(myDataFrame$Age)
summary(myDataFrame$Age)
boxplot.stats(myDataFrame$Age)
boxplot.stats(myDataFrame$Age)$out




